%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

% Font package that supports small caps and other font shapes
\usepackage{lmodern}  % Example: Use Latin Modern fonts

% FontAwesome package for icons
\usepackage{fontawesome5}

% Other packages
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Page style setup
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4pt}  % Set a suitable fooskip length

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0.1in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\ \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Resume content
\begin{document}

% Heading
\begin{center}
    {\Huge \scshape \textbf{Divya Sanvi}} \\ \vspace{4pt}
    \small +91 9799033486 $|$ \href{mailto:sanvidivya04@gmail.com}{\underline{sanvidivya04@gmail.com}} $|$ 
    \href{https://linkedin.com/in/divya-sanvi-ba8357262}{\underline{LinkedIn}} $|$ 
    \href{https://github.com/divyasanvi1}{\faIcon{github-square} \hspace{0.2em} {\underline{GitHub}}}
\end{center}

% Education section
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Hemvati Nandan Bahuguna Garhwal University}{7.32 CGPA}
      {B.Tech : Computer Science and Engineering (CSE)}{Aug. 2021 -- May 2025}
    \resumeSubheading
      {Gyan Bharti Model Residential Complex}{}
      {Class XII in PCM}{Aug. 2020}
\resumeSubHeadingListEnd

% Experience section
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Smart India Hackathon }{Apr. 2022 - Aug. 2022}
      {IIT Dhanbad, Dhanbad}{}
      \resumeItemListStart
        \resumeItem{Developed "Karmik," a MERN stack web application for the Government of India to trace migrant and unorganized laborers, supporting over \textbf{10,000} worker registrations and handling \textbf{5,000+} concurrent users.}
        \resumeItem{Led front-end development using React and Redux, reducing development time by \textbf{40\%} and improving data management efficiency.}
        \resumeItem{Optimized data retrieval speed by \textbf{30\%} with efficient API calls, enhancing user experience.}
        \resumeItem{Created features for workers to register and access \textbf{500+} government-provided internship and skill enhancement programs.}
        \resumeItem{Collaborated in a team of \textbf{6} developers over \textbf{4 months} to deliver the project.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

% Projects section
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{FlareFeed} $|$ \emph{JavaScript, Express.js, MongoDB, Node.js, Cloudinary, Postman}}{Sep. 2024}
    \resumeItemListStart
        \resumeItem{Developed a social media platform with features for video uploads, tweets, images, likes/dislikes, subscriptions, and comments.}
        \resumeItem{Implemented secure user authentication and authorization to enhance privacy and content security.}
        \resumeItem{Utilized Cloudinary for scalable media storage, reducing media load times by \textbf{40\%}.}
        \resumeItem{Built an admin dashboard for managing content and user activity, enabling real-time monitoring.}
        \resumeItem{Designed RESTful APIs and rigorously tested them using Postman, achieving \textbf{99.9\%} uptime reliability.}
        \resumeItem{Developed a scalable architecture capable of handling high concurrency with minimal latency.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Blog App} $|$ \emph{JavaScript, React, Redux, AppWrite, Material-UI, Tailwind-CSS}}{June 2023}
    \resumeItemListStart
        \resumeItem{Built a full-stack blog app with React.js frontend and Appwrite backend, designed to handle high traffic.}
        \resumeItem{Implemented features including user authentication, post creation, editing, and commenting.}
        \resumeItem{Optimized data handling with Appwrite and reduced frontend response time by \textbf{30\%} using React-Redux.}
        \resumeItem{Ensured a user-friendly experience with scalable architecture capable of handling significant traffic and user load with proper scaling and load balancing.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Recorder App} $|$ \emph{React, ReactMediaRecorder, MediaStreamApi, React-toastify, Material-UI, AppWrite}}{March 2023}
    \resumeItemListStart
        \resumeItem{Built a screen recording app with video, screen capture, audio functionalities, and user authentication.}
        \resumeItem{Created a responsive UI using Material-UI and optimized state management with React hooks and Redux, reducing response time by \textbf{25\%}.}
        \resumeItem{Added media download and real-time notifications with React-toastify, improving download speed and efficiency for an enhanced user experience.}
        \resumeItem{Ensured seamless performance, scalability, and user-friendly architecture with optimized tools.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% Technical skills section
\section{Technical Skills}
\begin{itemize}[leftmargin=0.1in, label={}]
    \small{
        \item \textbf{Languages:} C/C++, SQL, JavaScript, Python, Java*
        \item \textbf{Technologies/Frameworks:} React, Node.js, Express.js, jQuery, Appwrite
        \item \textbf{Database:} MongoDB Compass/Atlas, SQL
        \item \textbf{Cloud:} Amazon EC2, AWS S3, AWS CloudWatch, SQS, AWS Lambda
        \item \textbf{Developer Tools:} Git, GitHub, AWS, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse
    }
\end{itemize}

% Achievements section
\section{Achievements}
\begin{itemize}[leftmargin=0.2in]
 \item Solved \textbf{500+} DSA problems across different platforms (LeetCode, GFG)
 \item Achieved \textbf{5-star} rating in Problem Solving on HackerRank
 \item Achieved \textbf{5-star} rating in C++ on HackerRank
 \item \textbf{Smart India Hackathon Finalist 2022}
 \item \textbf{Invited as Smart India Hackathon Mentor 2024}
\end{itemize}



%--------------------------------
\end{document}
